Exposing Disputed Statements on the Web

### 2009-03-16 papers/uist_thinklink/thinklink.tex
Updated paper plan and tweaks to uist paper and notes

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}

@@

\abstract
We present DisagreeWeb, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue. As the user browses the web, DisagreeWeb highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on such a disputed claim then DisagreeWeb will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of DisagreeWeb.

@@

In this paper we present DisagreeWeb, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue. When DisagreeWeb is used as a browser plugin it will highlight text that makes a disputed claim. If a user clicks on such a highlighted snippet then DisagreeWeb presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of DisagreeWeb (Figure~\ref{claimview}). The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.

DisagreeWeb relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.

@@

DisagreeWeb layers an argumentation graph over the existing web.

>>>>

%\documentclass{article}
\documentclass{chi2009}
\usepackage{times}
%\usepackage{uist}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
% \usepackage[pdftex]{hyperref}
% \hypersetup{%
% pdftitle={Browsing the Web of Factual Claims},
% pdfauthor={Beth Trushkowsky and Rob Ennals},
% pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
% bookmarksnumbered,
% pdfstartview={FitH},
% colorlinks,
% citecolor=black,
% filecolor=black,
% linkcolor=black,
% urlcolor=black,
% breaklinks=true,
% }

@@

\abstract
We present Think Link, a browser extension that aims to let users see when the information they are reading presents only one side of a disputed issue. As the user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on such a disputed claim then Think Link will show tem an argument graph showing the best evidence for and against the claim being true, as determined by other users of Think Link.

@@

In this paper we present Think Link, a tool helps users discover when information they read is disputed or presents only one side of a contentious issue. When Think Link is used as a browser plugin it will highlight text that makes a disputed claim. If a user clicks on such a highlighted snippet then Think Link presents the user with an argument graph that shows the best evidence for and against the claim, as judged by other users of Think Link (Figure~\ref{claimview}). The argument graph contains links to snippets of text on other web sites that express conflicting or supporting points of view.

Think Link relies on users to identify disputed claims, to find appearances of these claims on web sites, and to vote for which snippets are most important.

@@

Think Link layers an argumentation graph over the existing web.
